Title: A proof-of-concept study

### 2022-01-07 paper.tex
update

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[Simulated count rate (photons s$^{-1}$ deg$^{-2}$) map in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection.]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray_0.8keV_angle_000.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{dddd}
    \label{fig_xray}
  \end{figure*}

>>>>

  %\begin{figure*}[ht]
  \begin{figure*}
    \subfigure[Synthetic count rate (photons s$^{-1}$ deg$^{-2}$) in the 0.6-1.0 keV range,\
               using a Hammer-Aitoff projection. Throughout this paper we show sky maps in\
               Galactic coordinates centered on the Galactic center.]
     {
      \includegraphics[width=\linewidth]{figures/fig__xray_0.8keV_angle_000.png}
      \label{fig__xray_0.8keV_angle_000}
     }
    \subfigure[Comparison of observed (black; \citealt{Predehl2020}) and simulated (red) one-dimensional\
               count rate profiles in the same energy band as \Cref{fig__xray_0.8keV_angle_000},\
               cut at various galactic latitudes (as labelled).]
     {
      \includegraphics[width=\linewidth]{figures/fig__x-ray-profile-0.8keV-000.png}
      \label{fig__x-ray-profile-0.8keV-000}
     }
    \caption{}
    \label{fig_xray}
  \end{figure*}
